Water, High-Altitude Condensates, and No Methane in the Atmosphere of the Warm Neptune WASP-107\lowercase{b}

### 2017-07-05 ms.tex
edits

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass[twocolumn]{aastex61}
\usepackage{natbib}

@@

\subsection{White Light Curve Fit}
To create the raw white light curve, we summed each spectrum over the 181 pixels in the spectral trace.  The white light curve has systematic trends that are typical for WFC3 observations \cite{zhou17}: the flux increases increases asymptotically over each orbit (the ``ramp" effect) and there is a visit-long linear trend. The largest ramp occurs in the initial orbit (orbit zero), so we only fit data from orbits one through four in our analysis, following common practice.  We fit the light curve with the analytic model of the form $F_\mathrm{white}(t) = S_\mathrm{white}(t)\times T_\mathrm{white}(t)$, where $S_\mathrm{white}$ is a systematics model and $T_\mathrm{white}$ is a transit model. We used the same systematics model as \cite{kreidberg15b}, Equation 1.  To model the transit, we used the \texttt{batman} package \citep{kreidberg15b}.  The transit model parameters are the orbital period $p$, time of inferior conjunction $t_0$, transit depth $r_p/r_s$, ratio of semi-major axis to stellar radius $a/r_s$, orbital inclination $i$, and the quadratic stellar limb darkening parameters $u_1$ and $u_2$.

@@

\subsubsection{Final Fit}
In our final fit, we fixed the transit parameters $a/r_s$, $i$, $p$ on the precise estimates from the Kepler light curve \cite{dai17}.  We also fixed the limb darkening parameters on predictions from a PHOENIX model for a star of FIXME properties, calculated with the FIXME package.  The remaining free parameters were $t_0$, $r_p/r_s$, and the systematics parameters for the visit-long and orbit-long trends.
%The model values are consistent with what we obtain from fitting for the limb darkening coefficients as free parameters.

@@

\section{Atmospheric Retrieval}
We use the CHIMERA chemically-consistent transmission retrieval tool described in \cite{kreidberg15} determine the basic atmospheric properties.   Briefly, the transmission spectrum solves the transmission geometry problem using the equations in \cite{brown11, tinetti12}.  We parametrize atmospheric composition with metallicity and carbon-to-oxygen ratio (C/O) under the assumption of thermochemical equilibrium using the NASA CEA routine \citep{gordon96} to compute the molecular abundances for H$_2$, He, H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, H$_2$S, Na, K, HCN, C$_2$H$_2$, TiO, VO, and FeH.    We have subsequently upgraded the transmission model to use correlated-K opacities \citep{lacis91, molliere15, amundsen16} for the aforementioned gases generated from the pre-tabulated line-by-line cross section database ($dv/v~10^6$) described in \cite{freedman14}. The transmission forward model is coupled with the powerful PyMultiNest tool \citep{buchner16} to solve the parameter estimation and model selection problems.

The nominal model set-up requires a temperature-pressure profile (parameterized via the \citealt{guillot10} relations), the atmospheric metallicity and carbon-to-oxygen ratio for molecular composition determination, disquilibrium properties crudely parameterized with nitrogen species and carbon species quench pressures \citep{morley17}, and aerosol properties.  We experiment with three atmospheric scenarios within this setup (Table XX):  Scenarios with and without methane, and with/without patchy cloud cover (as described and implemented in \citealt{line16}.  In all three scenarios we fix the T-P profile "shape" but scale the irradiation temperature, which incorporates unknown variables like the albedo and heat transport efficiency.  T-P profile shape information is not readily retrievable, nor does it strongly influence information derived from WFC3 transmission spectra \citep[e.g.][]{kreidberg15}. We also switch off the quench pressure parameters as they are unlikely to strongly influence the equilibrium abundance profiles of the spectrally prominent, nearly constant-with-altitude abundance, species like CH$_4$, H$_2$O, and NH$_3$ over this temperature range \citep[e.g.][]{line11, moses13}.  Aerosols are simply parameterized with a ``gray cloud top pressure" with the option for cloud patchiness. We do not consider ``sloped hazes" at this time as they are unlikely to influence the results.

@@

\bibliographystyle{apj}
\bibliography{ms.bib}

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass[twocolumn]{aastex61}

@@

\subsection{White Light Curve Fit}
To create the raw white light curve, we summed each spectrum over the 181 pixels in the spectral trace.  The white light curve has systematic trends that are typical for WFC3 observations \cite{zhou17}: the flux increases increases asymptotically over each orbit (the ``ramp" effect) and there is a visit-long linear trend. The largest ramp occurs in the initial orbit (orbit zero), so we only fit data from orbits one through four in our analysis, following common practice.  We fit the light curve with the analytic model of the form $F_\mathrm{white}(t) = S_\mathrm{white}(t)\times T_\mathrm{white}(t)$, where $S_\mathrm{white}$ is a systematics model and $T_\mathrm{white}$ is a transit model. We used the same systematics model as \cite{kreidberg15b}, Equation 1.  To model the transit, we used the \texttt{batman} package \citep{kreidberg15a}.  The transit model parameters are the orbital period $p$, time of inferior conjunction $t_0$, transit depth $r_p/r_s$, ratio of semi-major axis to stellar radius $a/r_s$, orbital inclination $i$, and the quadratic stellar limb darkening parameters $u_1$ and $u_2$.

@@

\subsubsection{Final Fit}
In our final fit, we fixed the transit parameters $a/r_s$, $i$, $p$ on the precise estimates from the Kepler light curve \citep{dai17}.  We also fixed the limb darkening parameters on predictions from a PHOENIX model for a star of FIXME properties, calculated with the FIXME package.  The remaining free parameters were $t_0$, $r_p/r_s$, and the systematics parameters for the visit-long and orbit-long trends.
%The model values are consistent with what we obtain from fitting for the limb darkening coefficients as free parameters.

@@

\section{Atmospheric Retrieval}
We use the CHIMERA chemically-consistent transmission retrieval tool described in \cite{kreidberg15b} to determine the basic atmospheric properties.   Briefly, the transmission spectrum solves the transmission geometry problem using the equations in \cite{brown01, tinetti12}.  We parametrize atmospheric composition with metallicity and carbon-to-oxygen ratio (C/O) under the assumption of thermochemical equilibrium using the NASA CEA routine \citep{gordon96} to compute the molecular abundances for H$_2$, He, H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, H$_2$S, Na, K, HCN, C$_2$H$_2$, TiO, VO, and FeH.    We have subsequently upgraded the transmission model to use correlated-K opacities \citep{lacis91, molliere15, amundsen16} for the aforementioned gases generated from the pre-tabulated line-by-line cross section database ($dv/v~10^6$) described in \cite{freedman14}. The transmission forward model is coupled with the powerful PyMultiNest tool \citep{buchner16} to solve the parameter estimation and model selection problems.

The nominal model set-up requires a temperature-pressure profile (parameterized via the \citealt{guillot10} relations), the atmospheric metallicity and carbon-to-oxygen ratio for molecular composition determination, disquilibrium properties crudely parameterized with nitrogen species and carbon species quench pressures \citep{morley17}, and aerosol properties.  We experiment with three atmospheric scenarios within this setup (Table XX):  Scenarios with and without methane, and with/without patchy cloud cover (as described and implemented in \citealt{line16}.  In all three scenarios we fix the T-P profile "shape" but scale the irradiation temperature, which incorporates unknown variables like the albedo and heat transport efficiency.  T-P profile shape information is not readily retrievable, nor does it strongly influence information derived from WFC3 transmission spectra \citep[e.g.][]{kreidberg15b}. We also switch off the quench pressure parameters as they are unlikely to strongly influence the equilibrium abundance profiles of the spectrally prominent, nearly constant-with-altitude abundance, species like CH$_4$, H$_2$O, and NH$_3$ over this temperature range \citep[e.g.][]{line11, moses13}.  Aerosols are simply parameterized with a ``gray cloud top pressure" with the option for cloud patchiness. We do not consider ``sloped hazes" at this time as they are unlikely to influence the results.

@@

\bibliographystyle{aasjournal}
\bibliography{ms.bib}
